Treatment planning for HDR Brachytherapy

### 2015-03-29 Paper Seminar/isim_paper.tex
found one mistake

\subsection{Body modle}
The body model is supplied as a three-dimensional array ("body array"), containing the type of the body cells, within a matlab file (.mat). The body array is set up as an equidistant point cloud of cells (1 unit $\widehat{=}$ 0.2cm), being transformed into 3D-array of voxels (compare algorithm \ref{model:voxel}). Besides the coordinate, a voxel contains several dosis variables (like extreme dosis, goal dosis) and the body type (normal tissue, spine, liver, pancreas and tumor tissue). \\
\begin{algorithm}[H]
maxDosis: \textit{double} [cGy] \\
minDosis: \textit{double} [cGy] \\
goalDosis: \textit{double} [cGy] \\
currentDosis: \textit{double} [cGy] \\
coordinate: \textit{Coordinate} [x: units, y: units, z: units] \\
bodyType: int
\label{model:voxel}
\caption{Properties of a voxel}
\end{algorithm}

>>>>

\subsection{Body model}
The body model is supplied as a three-dimensional array ("body array"), containing the type of the body cells, within a matlab file (.mat). The body array is set up as an equidistant point cloud of cells (1 unit $\widehat{=}$ 0.2cm), being transformed into 3D-array of voxels (compare algorithm \ref{model:voxel}). Besides the coordinate, a voxel contains several dosis variables (like extreme dosis, goal dosis) and the body type (normal tissue, spine, liver, pancreas and tumor tissue). \\
\begin{algorithm}[H]
maxDosis: \textit{double} [cGy] \\
minDosis: \textit{double} [cGy] \\
goalDosis: \textit{double} [cGy] \\
currentDosis: \textit{double} [cGy] \\
coordinate: \textit{Coordinate} [x: units, y: units, z: units] \\
bodyType: int
\label{model:voxel}
\caption{Properties of a voxel}
\end{algorithm}
